Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-04 Final-Draft.Rmd
changing stuff

---
title: ""
author: "Federico Chung, Will Madairy, Sofia Pozsonyiova, Quinn Rafferty"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    toc_float: true
bibliography: Library.bib
---

```{r, warning=FALSE, include=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)
library(gridExtra)
library(plotly)
library(janitor)
library(reshape2)
library(tidyr)
library(rstan)
library(rstanarm)
library(bayesplot)
```

@@

@@

# Introduction

Make sure to discuss the time period of interest 
## Project Motivations

## Project Goals

@@

# Data

## Data Descriptions

## Variables of interest

## Visualizations (Quinn)

@@

# Methods & Models (Feddy and Will)

## Markov Chain Algorithm

## Models of Interest

## Model Descriptions

@@

# Model Evaluation

## Model 1 Evaluation( Repeated measures)

## Model 2 Evaluation (Normal Regression)

## Model 3 Evaluation(Repeated Reg + Normal)

## Model 4 Evaluation (Longitudinal)

@@

# Results (Will)

## Posterior Predctions All States

### Table

## Posterior Prediction One State

## Final Model

# Conclusion

## Limitations

## Future Work

# Acknowledgments and References

>>>>

---
title: "Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics "
author: "Federico Chung, Will Madairy, Sofia Pozsonyiova, Quinn Rafferty"
date: 'May 8,2020'
output:
  html_document:
    toc: true
    toc_float: true
---

```{r, warning=FALSE, include=FALSE, message=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)
library(gridExtra)
library(plotly)
library(janitor)
library(reshape2)
library(tidyr)
library(rstan)
library(rstanarm)
library(bayesplot)
```

@@

# 1. Introduction

On March 17, 2020 President Trump referred to the Coronavirus as the "China Virus." Shortly after, the number of anti-Chinese incidents started to increase across the United States. One aspect of public health that is often thrown to the wayside is how influential public officials and leaders are in disseminating public health information. Moreover, not only can their words change the public's views on a health matter but it can also shift a nation's perspective on someone's identity. _[ADD SOME BACKGROUND LITERATURE THAT BACKS THIS CLAIM UP]_ In addition, given the influence of identity politics we may expect the term "China Virus" to be more polarizing to certain identities and states. _[ADD BACKGROUND LITERATURE + IDENTIFY SUBJECTS OF INTEREST]_. There are fewer studies devoted to analyzing these aspects of the pandemic.

Thus,our project aims to explore the relationship and variability of interest in the term "China Virus" across states through  political, demographic and COVID-19 characteristics. We ask the question, _[INSERT OUR RESERACH QUESTION]_ ?  In order to answer this question, we look to gain a better understanding of _[INSERT NAME OF BAYESIAN METHODOLOGY]_. Ultimately, we hope our research inspires others to explore and better understand the impact langauge and words have on the public during times of crisis.

\

# 2. Data

## 2.1 Data Descriptions

## 2.2 Variables of interest

## 2.3 Visualizations (Quinn)

@@

# 3. Methods & Models (Feddy and Will)

## 3.1 Markov Chain Algorithm

## 3.2 Models of Interest

## 3.3 Model Descriptions

@@

# 4. Model Evaluation

## 4.1 Model 1 Evaluation( Repeated measures)

## 4.2 Model 2 Evaluation (Normal Regression)

## 4.3 Model 3 Evaluation(Repeated Reg + Normal)

## 4.4 Model 4 Evaluation (Longitudinal)

@@

# 5. Results (Will)

## 5.1 Posterior Predctions All States

### 5.1.a Table

## 5.2 Posterior Prediction One State

## 5.3 Final Model

@@

# 6.Conclusion

## 6.1 Limitations

## 6.2 Future Work

@@

# 7. Acknowledgments and References
